Race Science in Mainstream Psychology, 1960-2010

### 2025-04-23 paper/paper.qmd
data and code DOI

The public analysis repository, <https://github.com/dhicks/race-science> *[DOI will go here]*, includes document metadata and documentwise counts of NLP-extracted noun phrases ("document-term matrices"), along with code to reproduce the analysis of the following sections.

@@

**Data and materials availability:** Web of Science search results and article fulltext are not publicly available due to intellectual property restrictions.  Preprocessed analysis data (document-term counts and article metadata) and analysis scripts are available at *[doi]*.

>>>>

The public analysis repository (<https://github.com/dhicks/race-science> and <https://doi.org/10.5281/zenodo.15272241>) includes document metadata and documentwise counts of NLP-extracted noun phrases ("document-term matrices"), along with code to reproduce the analysis of the following sections.

@@

**Data and materials availability:** Web of Science search results and article fulltext are not publicly available due to intellectual property restrictions.  Preprocessed analysis data (document-term counts and article metadata) and analysis scripts are available at <https://doi.org/10.5281/zenodo.15272241>.
